Adapting the Chumbley Score to match striae on Land Engraved Areas of bullets

### 2018-08-07 doc/paper.Rmd
update reference to aoas paper

---
title: "Adapting the Chumbley Score to match striae on Land Engraved Areas of bullets"
authors:
# - affiliation: Department of Statistics, Iowa State University 
- name: Ganesh Krishnan,
  degree: Master of Science (M.Sc.)
  # thank: The authors gratefully acknowledge funding from CSAFE through cooperative agreement \# 70NANB15H176 between NIST and Iowa State University. We would also like to thank the efforts of CSAFE and Roy J carver Microscopy lab in scanning the Hamby-44 set and providing the scans to us.
# - affiliation: Department of Statistics and CSAFE, Iowa State University 
- name: Prof. Heike Hofmann,
  degree: Doctor of Philosophy (Ph.D.)
affiliation: Department of Statistics, Iowa State University and CSAFE (Center for Statistics and Applications in Forensic Evidence)
funding: The authors gratefully acknowledge funding from CSAFE through cooperative agreement \# 70NANB15H176 between NIST and Iowa State University. 
thank: We would like to thank the efforts of CSAFE and Roy J Carver Microscopy lab in scanning the Hamby-44 set and providing the scans to us. We would also like to thank NIST for providing the Hamby-44 bullets to us for scanning.
presentedat:  This work was presented in the form of a poster in the AFTE 2018 49th Annual Training Seminar, held from June 3rd to June 8th, 2018 in Charleston, West Virginia
biblio-style: vancouver
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
    template: template.tex
  html_document: default
blinded: 0
keywords:
- forensic science
- toolmark
- cross-correlation
- Mann-Whitney U statistic
- land engraved areas (LEAs)
- algorithm
- signatures 
- same-source problem
bibliography: bibliography
abstract: The same-source problem remains a major challenge in forensic toolmark and firearm examination. Technological advances in surface imaging allow measurements of 3D surfaces at previously unforeseen resolutions and enable digitized imaging. Here, we investigate the applicability of the Chumbley scoring method \cite{hadler}, developed for screwdriver markings, for same-source identification of bullet striae. We provide methods to identify parameters that minimize the error rates for matching of LEAs using Hamby datasets 44 and 252 measured by NIST and CSAFE. We suggest a remedial algorithm to alleviate the problem of failed tests in the method, increasing both the power of the test and reducing error rates. Type II error rates of the proposed method improve by more than one third (Type I error of 0.05) and are on average about 0.22. This puts the proposed method on similar footing as other single feature matching approaches in the literature. 
---

>>>>

---
title: "Adapting the Chumbley Score to match striae on Land Engraved Areas of bullets"
authors:
# - affiliation: Department of Statistics, Iowa State University 
- name: Ganesh Krishnan,
  degree: Master of Science (M.Sc.)
  # thank: The authors gratefully acknowledge funding from CSAFE through cooperative agreement \# 70NANB15H176 between NIST and Iowa State University. We would also like to thank the efforts of CSAFE and Roy J carver Microscopy lab in scanning the Hamby-44 set and providing the scans to us.
# - affiliation: Department of Statistics and CSAFE, Iowa State University 
- name: Prof. Heike Hofmann,
  degree: Doctor of Philosophy (Ph.D.)
affiliation: Department of Statistics, Iowa State University and CSAFE (Center for Statistics and Applications in Forensic Evidence)
funding: The authors gratefully acknowledge funding from CSAFE through cooperative agreement \# 70NANB15H176 between NIST and Iowa State University. 
thank: We would like to thank the efforts of CSAFE and Roy J Carver Microscopy lab in scanning the Hamby-44 set and providing the scans to us. We would also like to thank NIST for providing the Hamby-44 bullets to us for scanning.
presentedat:  This work was presented in the form of a poster in the AFTE 2018 49th Annual Training Seminar, held from June 3rd to June 8th, 2018 in Charleston, West Virginia
biblio-style: jfs
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
    template: template.tex
  html_document: default
blinded: 0
keywords:
- forensic science
- toolmark
- cross-correlation
- Mann-Whitney U statistic
- land engraved areas (LEAs)
- algorithm
- signatures 
- same-source problem
bibliography: bibliography
abstract: The same-source problem remains a major challenge in forensic toolmark and firearm examination. Technological advances in surface imaging allow measurements of 3D surfaces at previously unforeseen resolutions and enable digitized imaging. Here, we investigate the applicability of the Chumbley scoring method \cite{hadler}, developed for screwdriver markings, for same-source identification of bullet striae. We provide methods to identify parameters that minimize the error rates for matching of LEAs using Hamby datasets 44 and 252 measured by NIST and CSAFE. We suggest a remedial algorithm to alleviate the problem of failed tests in the method, increasing both the power of the test and reducing error rates. Type II error rates of the proposed method improve by more than one third (Type I error of 0.05) and are on average about 0.22. This puts the proposed method on similar footing as other single feature matching approaches in the literature. 
---
